### 2018-09-28 ms.tex
Minor edits.

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
Our main performance metric was mean absolute error.
To assess how well the models are calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

Maps of the Indonesian input data_and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.

@@

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\section*{Acknowledgments}
Thanks everyone.
\nolinenumbers

>>>>

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
Our main performance metric was mean absolute error.
% Why not correlation
To assess how well the models are calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.

@@

%Summarise results

% Discuss and interpret. Generalise

% Short comings

% Future work

% Temporal model

% nonlinearities

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
%\paragraph*{S1 Fig.}
%\label{S1_Fig}
%{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\section*{Acknowledgments}
Thanks everyone.

\nolinenumbers
